---
title: "Data_explorations_primveg_anom_abun"
author: "Charlie Outhwaite"
date: "2023-01-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, cache = T)

# load libraries
library(ggplot2)
library(dplyr)
library(cowplot)
```


```{r data, echo = F}

# directories
datadir <- "5_RunLUIClimateModels/"
outdir <- "11_Explore_primveg/"
source("0_Functions.R")


# load in the dataset that includes the climate info
pred <- readRDS(file = paste0(datadir,"PREDICTSSitesClimate_Data.rds"))
pred <- droplevels(pred)

```

### Exploring the range of anomaly values


Table 1: The studies which have a large range in anomaly values across sites. Top 15 only.
```{r abun, echo=FALSE}

pred_sum <- pred %>% group_by(SS) %>% summarise(min = min(StdTmeanAnomaly), max = max(StdTmeanAnomaly), dif = (max(StdTmeanAnomaly- min(StdTmeanAnomaly))),
                                                min_ab = min(Total_abundance), max_ab = max(Total_abundance), 
                                                min_abRS = min(Total_abundance_RS), max_abRS = max(Total_abundance_RS))




knitr::kable(head(pred_sum %>% arrange(desc(dif)), 15))


```

### Plots exploring rescaled abundance

```{r expl plots, echo = F}

#### Exploratory plots ####


ggplot(pred) +
  geom_boxplot(aes(x = LUI, y = Total_abundance_RS)) + 
  theme_bw() + 
  ggtitle("Range of scaled abundance values by LUI")

# ggplot(pred) +
#   geom_boxplot(aes(x = LUI, y = Total_abundance), outlier.shape = NA) + 
#   ylim(0,300)+ 
#   theme_bw()


ggplot(pred) + 
  geom_point(aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS)) + 
  facet_wrap( ~ LUI)+ 
  theme_bw() + 
  ggtitle("Plot of anomaly against rescaled abundance, by LUI, all sites")


#View(pred[pred$LUI == "Primary vegetation" & pred$StdTmeanAnomalyRS >5,])

#View(pred[pred$StdTmeanAnomalyRS >5,])



```


There are 161 studies (out of 253) where the sites have different anomaly values. Although some of these differences are very small. 


### Looking at relationships



```{r range sites, echo = F}

# all sites
ggplot(pred, aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS)) + 
  geom_point() + 
  geom_smooth(method = lm) +
  facet_wrap( ~ LUI + Order)+ 
  theme_bw() + 
  ggtitle("All sites, split by order")



pred$SS <- as.character(pred$SS)
pred_sum$SS <- as.character(pred_sum$SS)

dif_sites <- pred_sum[pred_sum$dif>0,"SS" ]
dif_sites <- as.character(dif_sites$SS) # 161 studies

range_sites <- pred[pred$SS %in% dif_sites, ] # 6712 rows

#summary(range_sites$SS %in% dif_sites)

ggplot(range_sites) + 
  geom_point(aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS)) + 
  facet_wrap( ~ LUI)+ 
  theme_bw()+ 
  ggtitle("Sites where anomaly differs within study")


ggplot(range_sites, aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS)) + 
  geom_point() + 
  geom_smooth(method = lm) +
  facet_wrap( ~ LUI + Order)+ 
  theme_bw()+ 
  ggtitle("Sites where anomlay differs within study")


# 
# dif_sites <- pred_sum[pred_sum$dif>0.2,"SS" ]
# dif_sites <- as.character(dif_sites$SS)
# 
# range_sites <- pred[pred$SS %in% dif_sites, ] # 6712 rows
# range_sites <- droplevels(range_sites)
# 
# ggplot(range_sites) + 
#   geom_point(aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS)) + 
#   facet_wrap( ~ LUI)+ 
#   theme_bw()


dif_sites <- pred_sum[pred_sum$dif>0.4,"SS" ]
dif_sites <- as.character(dif_sites$SS)

range_sites <- pred[pred$SS %in% dif_sites, ] # 443 rows
range_sites <- droplevels(range_sites)

ggplot(range_sites, aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS)) + 
  geom_point() + 
  geom_smooth(method = lm) +
  facet_wrap( ~ LUI + Order)+ 
  theme_bw()+ 
  ggtitle("Sites where anomaly differs by more than 0.4 within study")



sites <- pred_sum[pred_sum$dif == 0,"SS" ]
sites <- as.character(sites$SS)

nonrange_sites <- pred[pred$SS %in% sites, ] # 2146 rows

ggplot(nonrange_sites, aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS)) + 
  geom_point() + 
  geom_smooth(method = lm) +
  facet_wrap( ~ LUI + Order)+ 
  theme_bw()+ 
  ggtitle("Sites where the anomaly does not differ between sites")


```
There are only 2146 sites from 92 studies where the anomaly value is exactly the same across all sites. 


```{r Lep slopes, echo = F}

lepdat <- pred[pred$Order == "Lepidoptera", ]


length(unique(lepdat$SS)) # 71 studies

ggplot(lepdat, aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS, col = SS)) + 
  geom_point() + 
  geom_smooth(method = lm) +
  facet_wrap(~ LUI) + 
  theme_bw()+ 
  ggtitle("") +
  theme(legend.position = "none")



lepdat_prim <- pred[pred$Order == "Lepidoptera" & pred$LUI == "Primary vegetation", ]


length(unique(lepdat_prim$SS)) # 38 studies

ggplot(lepdat_prim, aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS, col = SS)) + 
  geom_point() + 
  geom_smooth(method = lm, se = F) +
  theme_bw()+ 
  ggtitle("") +
  theme(legend.position = "none") +
  ylim(c(0, 1)) + 
  ggtitle("Includes all studies with Lep data in primary veg")


lep_prim_SS <- as.character(unique(lepdat_prim$SS)) # 38

View(pred_sum[pred_sum$SS %in% lep_prim_SS, ])


dif_leps <- pred_sum[pred_sum$SS %in% lep_prim_SS & !pred_sum$dif == 0, "SS"]


ggplot(lepdat_prim[lepdat_prim$SS %in% dif_leps$SS, ], aes(x = StdTmeanAnomalyRS, y = Total_abundance_RS, col = SS)) + 
  geom_point() + 
  geom_smooth(method = lm, se = F) +
  theme_bw()+ 
  ggtitle("") +
  theme(legend.position = "none") +
  ylim(c(0, 1))+ 
  ggtitle("Includes all studies with Lep data in primary veg which have a range of anom values")




```




### Just look at studies which have a primary vegetation reference site

Rerun models using just those Studies where there is a primary vegetation sites for reference. 

only 127 studies out of 253 have a primary vegetation site. 

```{r prim ref, echo = F}

# subset only studies where there is a primary vegetation site
studies <- unique(pred$SS) # 253

res <- NULL

for(i in studies){
  
  sub_pred <- pred[pred$SS == i, ]
  
  if("Primary vegetation" %in% sub_pred$LUI) prim <- TRUE else prim <- FALSE
  
  
  res <- rbind(res, c(i, prim))
  
}

res <- as.data.frame(res)

good_studies <- res[res$V2 == TRUE, "V1"] # 127 studies out of 253




```

```{r rerun1, echo = F}

# i. Abundance, mean anomaly

model_data <- pred[pred$SS %in% good_studies, ]
model_data <- model_data[!is.na(model_data$StdTmeanAnomalyRS), ] #4207 rows
model_data <- model_data[!is.na(model_data$LogAbund), ] # 3999 rows

model_data$SS <- as.factor(model_data$SS)


MeanAnomalyModelAbund <- GLMER(modelData = model_data,responseVar = "LogAbund",fitFamily = "gaussian",
                               fixedStruct = "LUI * StdTmeanAnomalyRS * Order",
                               randomStruct = "(1|SS)+(1|SSB)",
                               saveVars = c("SSBS"))

# get summary
#summary(MeanAnomalyModelAbund$model)


# save the model output
save(MeanAnomalyModelAbund, file = paste0(outdir, "MeanAnomalyModelAbund_primref.rdata"))


# ii. Richness, mean anomaly

model_data <- pred[pred$SS %in% good_studies, ] # 4207 rows

MeanAnomalyModelRich <- GLMER(modelData = model_data,responseVar = "Species_richness",fitFamily = "poisson",
                              fixedStruct = "LUI * StdTmeanAnomalyRS * Order",
                              randomStruct = "(1|SS)+(1|SSB)+(1|SSBS)",
                              saveVars = c("SSBS"))

#summary(MeanAnomalyModelRich$model)

save(MeanAnomalyModelRich, file = paste0(outdir, "MeanAnomalyModelRich_primref.rdata"))


```


### Plots for rerun of models using sites with a primary vegetation reference site


```{r primref plots, echo = F}

predictsSites <- pred

# set quantiles of predicted result to be presented in the plots
exclQuantiles <- c(0.025,0.975)

#### 1. Abundance, Mean Anomaly ####

nd <- expand.grid(
  StdTmeanAnomalyRS=seq(from = min(MeanAnomalyModelAbund$data$StdTmeanAnomalyRS),
                        to = max(MeanAnomalyModelAbund$data$StdTmeanAnomalyRS),
                        length.out = 100),
  LUI=factor(c("Primary vegetation","Secondary vegetation","Agriculture_Low","Agriculture_High"),
             levels = levels(MeanAnomalyModelAbund$data$LUI)),
  Order=factor(c("Coleoptera","Diptera","Hemiptera","Hymenoptera","Lepidoptera")))

# back transform the predictors
nd$StdTmeanAnomaly <- BackTransformCentreredPredictor(
  transformedX = nd$StdTmeanAnomalyRS,
  originalX = predictsSites$StdTmeanAnomaly)

# set richness and abundance to 0 - to be predicted
nd$LogAbund <- 0
nd$Species_richness <- 0

# reference for % difference = primary vegetation and positive anomaly closest to 0
refRow <- which((nd$LUI=="Primary vegetation") & (nd$StdTmeanAnomaly==min(abs(nd$StdTmeanAnomaly))))

# # set quantiles
# QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
#   MeanAnomalyModelAbund$data$LUI=="Primary vegetation"],
#   probs = exclQuantiles)
# QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
#   MeanAnomalyModelAbund$data$LUI=="Secondary vegetation"],
#   probs = exclQuantiles)
# QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
#   MeanAnomalyModelAbund$data$LUI=="Agriculture_Low"],
#   probs = exclQuantiles)
# QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
#   MeanAnomalyModelAbund$data$LUI=="Agriculture_High"],
#   probs = exclQuantiles)

# set quantiles by Order
# coleoptera
C_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Coleoptera"],
  probs = exclQuantiles)

# diptera
D_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Diptera"],
  probs = exclQuantiles)

# hemiptera
He_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Hemiptera"],
  probs = exclQuantiles)

# hymenoptera
Hy_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Hymenoptera"],
  probs = exclQuantiles)

# lepidoptera
L_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Lepidoptera"],
  probs = exclQuantiles)


# predict the results
a.preds.tmean <- PredictGLMERRandIter(model = MeanAnomalyModelAbund$model,data = nd)

# back transform the abundance values
a.preds.tmean <- exp(a.preds.tmean)-0.01

# create list of matrices
number_of_chunks = 5
list_a.preds.tmean <- lapply(seq(1, NROW(a.preds.tmean), ceiling(NROW(a.preds.tmean)/number_of_chunks)),
       function(i) a.preds.tmean[i:min(i + ceiling(NROW(a.preds.tmean)/number_of_chunks) - 1, NROW(a.preds.tmean)),])

# name them
names(list_a.preds.tmean) <- c("Coleoptera","Diptera","Hemiptera","Hymenoptera","Lepidoptera")
                             
# sweep out according to the refRow
list_a.preds.tmean <- lapply(list_a.preds.tmean,FUN=function(x){
 sweep (x=x, MARGIN = 2, STATS=x[refRow[1],],FUN="/") 
})


# print to global environment
list2env(list_a.preds.tmean,globalenv())

# split nd by order
Order<- paste0("nd_",nd$Order)
# create a list of data frames
by_Order <- split(nd,Order)
list2env(by_Order,globalenv())

# remove anything above and below the quantiles
Coleoptera[which((nd_Coleoptera$LUI=="Primary vegetation") & (nd_Coleoptera$StdTmeanAnomalyRS < C_QPV[1])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Primary vegetation") & (nd_Coleoptera$StdTmeanAnomalyRS > C_QPV[2])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Secondary vegetation") & (nd_Coleoptera$StdTmeanAnomalyRS < C_QSV[1])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Secondary vegetation") & (nd_Coleoptera$StdTmeanAnomalyRS > C_QSV[2])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Agriculture_Low") & (nd_Coleoptera$StdTmeanAnomalyRS < C_QAL[1])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Agriculture_Low") & (nd_Coleoptera$StdTmeanAnomalyRS > C_QAL[2])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Agriculture_High") & (nd_Coleoptera$StdTmeanAnomalyRS < C_QAH[1])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Agriculture_High") & (nd_Coleoptera$StdTmeanAnomalyRS > C_QAH[2])),] <- NA

Diptera[which((nd_Diptera$LUI=="Primary vegetation") & (nd_Diptera$StdTmeanAnomalyRS < D_QPV[1])),] <- NA
Diptera[which((nd_Diptera$LUI=="Primary vegetation") & (nd_Diptera$StdTmeanAnomalyRS > D_QPV[2])),] <- NA
Diptera[which((nd_Diptera$LUI=="Secondary vegetation") & (nd_Diptera$StdTmeanAnomalyRS < D_QSV[1])),] <- NA
Diptera[which((nd_Diptera$LUI=="Secondary vegetation") & (nd_Diptera$StdTmeanAnomalyRS > D_QSV[2])),] <- NA
Diptera[which((nd_Diptera$LUI=="Agriculture_Low") & (nd_Diptera$StdTmeanAnomalyRS < D_QAL[1])),] <- NA
Diptera[which((nd_Diptera$LUI=="Agriculture_Low") & (nd_Diptera$StdTmeanAnomalyRS > D_QAL[2])),] <- NA
Diptera[which((nd_Diptera$LUI=="Agriculture_High") & (nd_Diptera$StdTmeanAnomalyRS < D_QAH[1])),] <- NA
Diptera[which((nd_Diptera$LUI=="Agriculture_High") & (nd_Diptera$StdTmeanAnomalyRS > D_QAH[2])),] <- NA

Hemiptera[which((nd_Hemiptera$LUI=="Primary vegetation") & (nd_Hemiptera$StdTmeanAnomalyRS < He_QPV[1])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Primary vegetation") & (nd_Hemiptera$StdTmeanAnomalyRS > He_QPV[2])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Secondary vegetation") & (nd_Hemiptera$StdTmeanAnomalyRS < He_QSV[1])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Secondary vegetation") & (nd_Hemiptera$StdTmeanAnomalyRS > He_QSV[2])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Agriculture_Low") & (nd_Hemiptera$StdTmeanAnomalyRS < He_QAL[1])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Agriculture_Low") & (nd_Hemiptera$StdTmeanAnomalyRS > He_QAL[2])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Agriculture_High") & (nd_Hemiptera$StdTmeanAnomalyRS < He_QAH[1])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Agriculture_High") & (nd_Hemiptera$StdTmeanAnomalyRS > He_QAH[2])),] <- NA

Hymenoptera[which((nd_Hymenoptera$LUI=="Primary vegetation") & (nd_Hymenoptera$StdTmeanAnomalyRS < Hy_QPV[1])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Primary vegetation") & (nd_Hymenoptera$StdTmeanAnomalyRS > Hy_QPV[2])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Secondary vegetation") & (nd_Hymenoptera$StdTmeanAnomalyRS < Hy_QSV[1])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Secondary vegetation") & (nd_Hymenoptera$StdTmeanAnomalyRS > Hy_QSV[2])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Agriculture_Low") & (nd_Hymenoptera$StdTmeanAnomalyRS < Hy_QAL[1])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Agriculture_Low") & (nd_Hymenoptera$StdTmeanAnomalyRS > Hy_QAL[2])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Agriculture_High") & (nd_Hymenoptera$StdTmeanAnomalyRS < Hy_QAH[1])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Agriculture_High") & (nd_Hymenoptera$StdTmeanAnomalyRS > Hy_QAH[2])),] <- NA

Lepidoptera[which((nd_Lepidoptera$LUI=="Primary vegetation") & (nd_Lepidoptera$StdTmeanAnomalyRS < L_QPV[1])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Primary vegetation") & (nd_Lepidoptera$StdTmeanAnomalyRS > L_QPV[2])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Secondary vegetation") & (nd_Lepidoptera$StdTmeanAnomalyRS < L_QSV[1])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Secondary vegetation") & (nd_Lepidoptera$StdTmeanAnomalyRS > L_QSV[2])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Agriculture_Low") & (nd_Lepidoptera$StdTmeanAnomalyRS < L_QAL[1])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Agriculture_Low") & (nd_Lepidoptera$StdTmeanAnomalyRS > L_QAL[2])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Agriculture_High") & (nd_Lepidoptera$StdTmeanAnomalyRS < L_QAH[1])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Agriculture_High") & (nd_Lepidoptera$StdTmeanAnomalyRS > L_QAH[2])),] <- NA


# Get the median, upper and lower quants for the plot

nd_Coleoptera$PredMedian <- ((apply(X = Coleoptera,MARGIN = 1,
                                    FUN = median,na.rm=TRUE))*100)-100
nd_Coleoptera$PredUpper <- ((apply(X = Coleoptera,MARGIN = 1,
                                   FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Coleoptera$PredLower <- ((apply(X = Coleoptera,MARGIN = 1,
                                   FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd_Diptera$PredMedian <- ((apply(X = Diptera,MARGIN = 1,
                                 FUN = median,na.rm=TRUE))*100)-100
nd_Diptera$PredUpper <- ((apply(X = Diptera,MARGIN = 1,
                                FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Diptera$PredLower <- ((apply(X = Diptera,MARGIN = 1,
                                FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd_Hemiptera$PredMedian <- ((apply(X = Hemiptera,MARGIN = 1,
                                   FUN = median,na.rm=TRUE))*100)-100
nd_Hemiptera$PredUpper <- ((apply(X = Hemiptera,MARGIN = 1,
                                  FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Hemiptera$PredLower <- ((apply(X = Hemiptera,MARGIN = 1,
                                  FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd_Hymenoptera$PredMedian <- ((apply(X = Hymenoptera,MARGIN = 1,
                                     FUN = median,na.rm=TRUE))*100)-100
nd_Hymenoptera$PredUpper <- ((apply(X = Hymenoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Hymenoptera$PredLower <- ((apply(X = Hymenoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd_Lepidoptera$PredMedian <- ((apply(X = Lepidoptera,MARGIN = 1,
                                     FUN = median,na.rm=TRUE))*100)-100
nd_Lepidoptera$PredUpper <- ((apply(X = Lepidoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Lepidoptera$PredLower <- ((apply(X = Lepidoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100


# set factor levels
nd_Coleoptera$LUI <- factor(nd_Coleoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd_Diptera$LUI <- factor(nd_Diptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd_Hemiptera$LUI <- factor(nd_Hemiptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd_Hymenoptera$LUI <- factor(nd_Hymenoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd_Lepidoptera$LUI <- factor(nd_Lepidoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))

# plot

p_coleoptera <- ggplot(data = nd_Coleoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Coleoptera$PredLower, ymax = nd_Coleoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") + 
  ggtitle("Coleoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none", 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25)) 
  

p_diptera <- ggplot(data = nd_Diptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Diptera$PredLower, ymax = nd_Diptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Diptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none", 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25)) 
  

p_hemiptera <- ggplot(data = nd_Hemiptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Hemiptera$PredLower, ymax = nd_Hemiptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Hemiptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25))
  

p_hymenoptera <- ggplot(data = nd_Hymenoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Hymenoptera$PredLower, ymax = nd_Hymenoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Hymenoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none", 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25))

p_lepidoptera <- ggplot(data = nd_Lepidoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Lepidoptera$PredLower, ymax = nd_Lepidoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Lepidoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25)) 
  

# get the legend
legend <- get_legend(
  p_coleoptera +
    guides(color = guide_legend(ncol = 1)) +
    theme(legend.position = "right",
          legend.background = element_blank(), 
          legend.text = element_text(size = 7), 
          legend.title = element_blank())
)


# put them all together to save them
MeanAnomAbund <- cowplot::plot_grid(p_coleoptera,p_diptera,p_hemiptera,p_hymenoptera,p_lepidoptera,legend, ncol=3)
MeanAnomAbund
# save plot (pdf)
ggsave(filename = paste0(outdir, "MeanAnomAbund_primref.pdf"), plot = MeanAnomAbund, width = 200, height = 150, units = "mm", dpi = 300)

# save plot (jpeg)
ggsave("MeanAnomAbund_primref.jpeg", device ="jpeg", path = outdir, width=20, height=15, units="cm", dpi = 350)


#### 2. Richness, Mean Anomaly ####

nd2 <- expand.grid(
  StdTmeanAnomalyRS=seq(from = min(MeanAnomalyModelRich$data$StdTmeanAnomalyRS),
                        to = max(MeanAnomalyModelRich$data$StdTmeanAnomalyRS),
                        length.out = 100),
  LUI=factor(c("Primary vegetation","Secondary vegetation","Agriculture_Low","Agriculture_High"),
             levels = levels(MeanAnomalyModelRich$data$LUI)),
  Order=factor(c("Coleoptera","Diptera","Hemiptera","Hymenoptera","Lepidoptera")))

# back transform the predictors
nd2$StdTmeanAnomaly <- BackTransformCentreredPredictor(
  transformedX = nd2$StdTmeanAnomalyRS,
  originalX = predictsSites$StdTmeanAnomaly)

# set richness and abundance to 0 - to be predicted
nd2$LogAbund <- 0
nd2$Species_richness <- 0

# reference for % difference = primary vegetation and positive anomaly closest to 0
refRow <- which((nd2$LUI=="Primary vegetation") & (nd2$StdTmeanAnomaly==min(abs(nd2$StdTmeanAnomaly))))

# set quantiles
# coleoptera
C_QPV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Primary vegetation" & MeanAnomalyModelRich$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QSV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Secondary vegetation" & MeanAnomalyModelRich$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QAL <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_Low" & MeanAnomalyModelRich$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QAH <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_High" & MeanAnomalyModelRich$data$Order == "Coleoptera"],
  probs = exclQuantiles)

# diptera
D_QPV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Primary vegetation" & MeanAnomalyModelRich$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QSV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Secondary vegetation" & MeanAnomalyModelRich$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QAL <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_Low" & MeanAnomalyModelRich$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QAH <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_High" & MeanAnomalyModelRich$data$Order == "Diptera"],
  probs = exclQuantiles)

# hemiptera
He_QPV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Primary vegetation" & MeanAnomalyModelRich$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QSV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Secondary vegetation" & MeanAnomalyModelRich$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QAL <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_Low" & MeanAnomalyModelRich$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QAH <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_High" & MeanAnomalyModelRich$data$Order == "Hemiptera"],
  probs = exclQuantiles)

# hymenoptera
Hy_QPV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Primary vegetation" & MeanAnomalyModelRich$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QSV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Secondary vegetation" & MeanAnomalyModelRich$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QAL <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_Low" & MeanAnomalyModelRich$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QAH <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_High" & MeanAnomalyModelRich$data$Order == "Hymenoptera"],
  probs = exclQuantiles)

# lepidoptera
L_QPV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Primary vegetation" & MeanAnomalyModelRich$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QSV <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Secondary vegetation" & MeanAnomalyModelRich$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QAL <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_Low" & MeanAnomalyModelRich$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QAH <- quantile(x = MeanAnomalyModelRich$data$StdTmeanAnomalyRS[
  MeanAnomalyModelRich$data$LUI=="Agriculture_High" & MeanAnomalyModelRich$data$Order == "Lepidoptera"],
  probs = exclQuantiles)


# predict the results
sr.preds.tmean <- PredictGLMERRandIter(model = MeanAnomalyModelRich$model,data = nd2)

# back transform the abundance values
sr.preds.tmean <- exp(sr.preds.tmean)-0.01

# create list of matrices
number_of_chunks = 5
list_sr.preds.tmean <- lapply(seq(1, NROW(sr.preds.tmean), ceiling(NROW(sr.preds.tmean)/number_of_chunks)),
                              function(i) sr.preds.tmean[i:min(i + ceiling(NROW(sr.preds.tmean)/number_of_chunks) - 1, NROW(sr.preds.tmean)),])
# name them
names(list_sr.preds.tmean) <- c("Coleoptera","Diptera","Hemiptera","Hymenoptera","Lepidoptera")

# sweep out according to the refRow
list_sr.preds.tmean <- lapply(list_sr.preds.tmean,FUN=function(x){
  sweep (x=x, MARGIN = 2, STATS=x[refRow[1],],FUN="/") 
})
                              
list2env(list_sr.preds.tmean,globalenv())

# split nd by order
Order<- paste0("nd2_",nd2$Order)
# create a list of data frames
by_Order <- split(nd2,Order)
list2env(by_Order,globalenv())

# remove anything above and below the quantiles
Coleoptera[which((nd2_Coleoptera$LUI=="Primary vegetation") & (nd2_Coleoptera$StdTmeanAnomalyRS < C_QPV[1])),] <- NA
Coleoptera[which((nd2_Coleoptera$LUI=="Primary vegetation") & (nd2_Coleoptera$StdTmeanAnomalyRS > C_QPV[2])),] <- NA
Coleoptera[which((nd2_Coleoptera$LUI=="Secondary vegetation") & (nd2_Coleoptera$StdTmeanAnomalyRS < C_QSV[1])),] <- NA
Coleoptera[which((nd2_Coleoptera$LUI=="Secondary vegetation") & (nd2_Coleoptera$StdTmeanAnomalyRS > C_QSV[2])),] <- NA
Coleoptera[which((nd2_Coleoptera$LUI=="Agriculture_Low") & (nd2_Coleoptera$StdTmeanAnomalyRS < C_QAL[1])),] <- NA
Coleoptera[which((nd2_Coleoptera$LUI=="Agriculture_Low") & (nd2_Coleoptera$StdTmeanAnomalyRS > C_QAL[2])),] <- NA
Coleoptera[which((nd2_Coleoptera$LUI=="Agriculture_High") & (nd2_Coleoptera$StdTmeanAnomalyRS < C_QAH[1])),] <- NA
Coleoptera[which((nd2_Coleoptera$LUI=="Agriculture_High") & (nd2_Coleoptera$StdTmeanAnomalyRS > C_QAH[2])),] <- NA

Diptera[which((nd2_Diptera$LUI=="Primary vegetation") & (nd2_Diptera$StdTmeanAnomalyRS < D_QPV[1])),] <- NA
Diptera[which((nd2_Diptera$LUI=="Primary vegetation") & (nd2_Diptera$StdTmeanAnomalyRS > D_QPV[2])),] <- NA
Diptera[which((nd2_Diptera$LUI=="Secondary vegetation") & (nd2_Diptera$StdTmeanAnomalyRS < D_QSV[1])),] <- NA
Diptera[which((nd2_Diptera$LUI=="Secondary vegetation") & (nd2_Diptera$StdTmeanAnomalyRS > D_QSV[2])),] <- NA
Diptera[which((nd2_Diptera$LUI=="Agriculture_Low") & (nd2_Diptera$StdTmeanAnomalyRS < D_QAL[1])),] <- NA
Diptera[which((nd2_Diptera$LUI=="Agriculture_Low") & (nd2_Diptera$StdTmeanAnomalyRS > D_QAL[2])),] <- NA
Diptera[which((nd2_Diptera$LUI=="Agriculture_High") & (nd2_Diptera$StdTmeanAnomalyRS < D_QAH[1])),] <- NA
Diptera[which((nd2_Diptera$LUI=="Agriculture_High") & (nd2_Diptera$StdTmeanAnomalyRS > D_QAH[2])),] <- NA

Hemiptera[which((nd2_Hemiptera$LUI=="Primary vegetation") & (nd2_Hemiptera$StdTmeanAnomalyRS < He_QPV[1])),] <- NA
Hemiptera[which((nd2_Hemiptera$LUI=="Primary vegetation") & (nd2_Hemiptera$StdTmeanAnomalyRS > He_QPV[2])),] <- NA
Hemiptera[which((nd2_Hemiptera$LUI=="Secondary vegetation") & (nd2_Hemiptera$StdTmeanAnomalyRS < He_QSV[1])),] <- NA
Hemiptera[which((nd2_Hemiptera$LUI=="Secondary vegetation") & (nd2_Hemiptera$StdTmeanAnomalyRS > He_QSV[2])),] <- NA
Hemiptera[which((nd2_Hemiptera$LUI=="Agriculture_Low") & (nd2_Hemiptera$StdTmeanAnomalyRS < He_QAL[1])),] <- NA
Hemiptera[which((nd2_Hemiptera$LUI=="Agriculture_Low") & (nd2_Hemiptera$StdTmeanAnomalyRS > He_QAL[2])),] <- NA
Hemiptera[which((nd2_Hemiptera$LUI=="Agriculture_High") & (nd2_Hemiptera$StdTmeanAnomalyRS < He_QAH[1])),] <- NA
Hemiptera[which((nd2_Hemiptera$LUI=="Agriculture_High") & (nd2_Hemiptera$StdTmeanAnomalyRS > He_QAH[2])),] <- NA

Hymenoptera[which((nd2_Hymenoptera$LUI=="Primary vegetation") & (nd2_Hymenoptera$StdTmeanAnomalyRS < Hy_QPV[1])),] <- NA
Hymenoptera[which((nd2_Hymenoptera$LUI=="Primary vegetation") & (nd2_Hymenoptera$StdTmeanAnomalyRS > Hy_QPV[2])),] <- NA
Hymenoptera[which((nd2_Hymenoptera$LUI=="Secondary vegetation") & (nd2_Hymenoptera$StdTmeanAnomalyRS < Hy_QSV[1])),] <- NA
Hymenoptera[which((nd2_Hymenoptera$LUI=="Secondary vegetation") & (nd2_Hymenoptera$StdTmeanAnomalyRS > Hy_QSV[2])),] <- NA
Hymenoptera[which((nd2_Hymenoptera$LUI=="Agriculture_Low") & (nd2_Hymenoptera$StdTmeanAnomalyRS < Hy_QAL[1])),] <- NA
Hymenoptera[which((nd2_Hymenoptera$LUI=="Agriculture_Low") & (nd2_Hymenoptera$StdTmeanAnomalyRS > Hy_QAL[2])),] <- NA
Hymenoptera[which((nd2_Hymenoptera$LUI=="Agriculture_High") & (nd2_Hymenoptera$StdTmeanAnomalyRS < Hy_QAH[1])),] <- NA
Hymenoptera[which((nd2_Hymenoptera$LUI=="Agriculture_High") & (nd2_Hymenoptera$StdTmeanAnomalyRS > Hy_QAH[2])),] <- NA

Lepidoptera[which((nd2_Lepidoptera$LUI=="Primary vegetation") & (nd2_Lepidoptera$StdTmeanAnomalyRS < L_QPV[1])),] <- NA
Lepidoptera[which((nd2_Lepidoptera$LUI=="Primary vegetation") & (nd2_Lepidoptera$StdTmeanAnomalyRS > L_QPV[2])),] <- NA
Lepidoptera[which((nd2_Lepidoptera$LUI=="Secondary vegetation") & (nd2_Lepidoptera$StdTmeanAnomalyRS < L_QSV[1])),] <- NA
Lepidoptera[which((nd2_Lepidoptera$LUI=="Secondary vegetation") & (nd2_Lepidoptera$StdTmeanAnomalyRS > L_QSV[2])),] <- NA
Lepidoptera[which((nd2_Lepidoptera$LUI=="Agriculture_Low") & (nd2_Lepidoptera$StdTmeanAnomalyRS < L_QAL[1])),] <- NA
Lepidoptera[which((nd2_Lepidoptera$LUI=="Agriculture_Low") & (nd2_Lepidoptera$StdTmeanAnomalyRS > L_QAL[2])),] <- NA
Lepidoptera[which((nd2_Lepidoptera$LUI=="Agriculture_High") & (nd2_Lepidoptera$StdTmeanAnomalyRS < L_QAH[1])),] <- NA
Lepidoptera[which((nd2_Lepidoptera$LUI=="Agriculture_High") & (nd2_Lepidoptera$StdTmeanAnomalyRS > L_QAH[2])),] <- NA



# Get the median, upper and lower quants for the plot
nd2_Coleoptera$PredMedian <- ((apply(X = Coleoptera,MARGIN = 1,
                                     FUN = median,na.rm=TRUE))*100)-100
nd2_Coleoptera$PredUpper <- ((apply(X = Coleoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd2_Coleoptera$PredLower <- ((apply(X = Coleoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd2_Diptera$PredMedian <- ((apply(X = Diptera,MARGIN = 1,
                                  FUN = median,na.rm=TRUE))*100)-100
nd2_Diptera$PredUpper <- ((apply(X = Diptera,MARGIN = 1,
                                 FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd2_Diptera$PredLower <- ((apply(X = Diptera,MARGIN = 1,
                                 FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd2_Hemiptera$PredMedian <- ((apply(X = Hemiptera,MARGIN = 1,
                                    FUN = median,na.rm=TRUE))*100)-100
nd2_Hemiptera$PredUpper <- ((apply(X = Hemiptera,MARGIN = 1,
                                   FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd2_Hemiptera$PredLower <- ((apply(X = Hemiptera,MARGIN = 1,
                                   FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd2_Hymenoptera$PredMedian <- ((apply(X = Hymenoptera,MARGIN = 1,
                                      FUN = median,na.rm=TRUE))*100)-100
nd2_Hymenoptera$PredUpper <- ((apply(X = Hymenoptera,MARGIN = 1,
                                     FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd2_Hymenoptera$PredLower <- ((apply(X = Hymenoptera,MARGIN = 1,
                                     FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd2_Lepidoptera$PredMedian <- ((apply(X = Lepidoptera,MARGIN = 1,
                                      FUN = median,na.rm=TRUE))*100)-100
nd2_Lepidoptera$PredUpper <- ((apply(X = Lepidoptera,MARGIN = 1,
                                     FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd2_Lepidoptera$PredLower <- ((apply(X = Lepidoptera,MARGIN = 1,
                                     FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100


# set factor levels
nd2_Coleoptera$LUI <- factor(nd2_Coleoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd2_Diptera$LUI <- factor(nd2_Diptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd2_Hemiptera$LUI <- factor(nd2_Hemiptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd2_Hymenoptera$LUI <- factor(nd2_Hymenoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd2_Lepidoptera$LUI <- factor(nd2_Lepidoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))

# plot
p_coleoptera <- ggplot(data = nd2_Coleoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd2_Coleoptera$PredLower, ymax = nd2_Coleoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in species richness (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Coleoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25)) 

p_diptera <- ggplot(data = nd2_Diptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd2_Diptera$PredLower, ymax = nd2_Diptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in species richness (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Diptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none", 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25))

p_hemiptera <- ggplot(data = nd2_Hemiptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd2_Hemiptera$PredLower, ymax = nd2_Hemiptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  #scale_y_continuous(breaks = c(-100, 0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000), limits = c(-100, 1000)) +
  ylab("Change in species richness (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Hemiptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25))

p_hymenoptera <- ggplot(data = nd2_Hymenoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd2_Hymenoptera$PredLower, ymax = nd2_Hymenoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  #scale_y_continuous(breaks = c(-100, 0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000), limits = c(-100, 1000)) +
  ylab("Change in species richness (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Hymenoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none",
        #legend.position = c(0.2, 0.8),
        #legend.background = element_blank(), 
        #legend.text = element_text(size = 6), 
        #legend.title = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25))

p_lepidoptera <- ggplot(data = nd2_Lepidoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd2_Lepidoptera$PredLower, ymax = nd2_Lepidoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  #scale_y_continuous(breaks = c(-100, 0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000), limits = c(-100, 1000)) +
  ylab("Change in species richness (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Lepidoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none", 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25)) 

# get the legend
legend <- get_legend(
  p_coleoptera +
    guides(color = guide_legend(ncol = 1)) +
    theme(legend.position = "right",
          legend.background = element_blank(), 
          legend.text = element_text(size = 7), 
          legend.title = element_blank())
)


# put them all together to save them
MeanAnomRich <- cowplot::plot_grid(p_coleoptera,p_diptera,p_hemiptera,p_hymenoptera,p_lepidoptera,legend, ncol=3)
MeanAnomRich
# save plot (pdf)
ggsave(filename = paste0(outdir, "MeanAnomRich_primref.pdf"), plot = MeanAnomRich, width = 200, height = 150, units = "mm", dpi = 300)

# save plot (jpeg)
ggsave("MeanAnomRich_primref.jpeg", device ="jpeg", path = outdir, width=20, height=15, units="cm", dpi = 350)


```

Primary vegetation tends to follow the same patterns as previously. One obvious difference is the line for Lep species richness in primary vegetation. 





### Sequentially remove studies which have arange of anomaly values

Here, I sequentially reran the analysis each time removing studies where the differences in anomaly values across sites was gradually reduced to 0. 

*Differences between anomaly values within a study range from 0 to 1.05*

```{r seq run, echo = F}

runs <- seq(from = 0, to = 1, by = 0.2)


for(i in runs){
  
  # get a list of studies that are to be including 
  
  pred_sum_sub <- pred_sum[pred_sum$dif > i, ]
  studies_to_exc <- pred_sum_sub$SS
  
# i. Abundance, mean anomaly

model_data <- pred[!pred$SS %in% studies_to_exc, ]
model_data <- model_data[!is.na(model_data$StdTmeanAnomalyRS), ] 
model_data <- model_data[!is.na(model_data$LogAbund), ] 

model_data$SS <- as.factor(model_data$SS)

 
MeanAnomalyModelAbund <- GLMER(modelData = model_data,responseVar = "LogAbund",fitFamily = "gaussian",
                               fixedStruct = "LUI * StdTmeanAnomalyRS * Order",
                               randomStruct = "(1|SS)+(1|SSB)",
                               saveVars = c("SSBS")) 


# save the model output
save(MeanAnomalyModelAbund, file = paste0(outdir, "MeanAnomalyModelAbund_excl_", i, ".rdata"))


predictsSites <- pred

# set quantiles of predicted result to be presented in the plots
exclQuantiles <- c(0.025,0.975)

#### 1. Abundance, Mean Anomaly ####

nd <- expand.grid(
  StdTmeanAnomalyRS=seq(from = min(MeanAnomalyModelAbund$data$StdTmeanAnomalyRS),
                        to = max(MeanAnomalyModelAbund$data$StdTmeanAnomalyRS),
                        length.out = 100),
  LUI=factor(c("Primary vegetation","Secondary vegetation","Agriculture_Low","Agriculture_High"),
             levels = levels(MeanAnomalyModelAbund$data$LUI)),
  Order=factor(c("Coleoptera","Diptera","Hemiptera","Hymenoptera","Lepidoptera")))

# back transform the predictors
nd$StdTmeanAnomaly <- BackTransformCentreredPredictor(
  transformedX = nd$StdTmeanAnomalyRS,
  originalX = predictsSites$StdTmeanAnomaly)

# set richness and abundance to 0 - to be predicted
nd$LogAbund <- 0
nd$Species_richness <- 0

# reference for % difference = primary vegetation and positive anomaly closest to 0
refRow <- which((nd$LUI=="Primary vegetation") & (nd$StdTmeanAnomaly==min(abs(nd$StdTmeanAnomaly))))

# # set quantiles
# QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
#   MeanAnomalyModelAbund$data$LUI=="Primary vegetation"],
#   probs = exclQuantiles)
# QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
#   MeanAnomalyModelAbund$data$LUI=="Secondary vegetation"],
#   probs = exclQuantiles)
# QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
#   MeanAnomalyModelAbund$data$LUI=="Agriculture_Low"],
#   probs = exclQuantiles)
# QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
#   MeanAnomalyModelAbund$data$LUI=="Agriculture_High"],
#   probs = exclQuantiles)

# set quantiles by Order
# coleoptera
C_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Coleoptera"],
  probs = exclQuantiles)
C_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Coleoptera"],
  probs = exclQuantiles)

# diptera
D_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Diptera"],
  probs = exclQuantiles)
D_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Diptera"],
  probs = exclQuantiles)

# hemiptera
He_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Hemiptera"],
  probs = exclQuantiles)
He_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Hemiptera"],
  probs = exclQuantiles)

# hymenoptera
Hy_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Hymenoptera"],
  probs = exclQuantiles)
Hy_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Hymenoptera"],
  probs = exclQuantiles)

# lepidoptera
L_QPV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Primary vegetation" & MeanAnomalyModelAbund$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QSV <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Secondary vegetation" & MeanAnomalyModelAbund$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QAL <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_Low" & MeanAnomalyModelAbund$data$Order == "Lepidoptera"],
  probs = exclQuantiles)
L_QAH <- quantile(x = MeanAnomalyModelAbund$data$StdTmeanAnomalyRS[
  MeanAnomalyModelAbund$data$LUI=="Agriculture_High" & MeanAnomalyModelAbund$data$Order == "Lepidoptera"],
  probs = exclQuantiles)


# predict the results
a.preds.tmean <- PredictGLMERRandIter(model = MeanAnomalyModelAbund$model,data = nd)

# back transform the abundance values
a.preds.tmean <- exp(a.preds.tmean)-0.01

# create list of matrices
number_of_chunks = 5
list_a.preds.tmean <- lapply(seq(1, NROW(a.preds.tmean), ceiling(NROW(a.preds.tmean)/number_of_chunks)),
       function(i) a.preds.tmean[i:min(i + ceiling(NROW(a.preds.tmean)/number_of_chunks) - 1, NROW(a.preds.tmean)),])

# name them
names(list_a.preds.tmean) <- c("Coleoptera","Diptera","Hemiptera","Hymenoptera","Lepidoptera")
                             
# sweep out according to the refRow
list_a.preds.tmean <- lapply(list_a.preds.tmean,FUN=function(x){
 sweep (x=x, MARGIN = 2, STATS=x[refRow[1],],FUN="/") 
})


# print to global environment
list2env(list_a.preds.tmean,globalenv())

# split nd by order
Order<- paste0("nd_",nd$Order)
# create a list of data frames
by_Order <- split(nd,Order)
list2env(by_Order,globalenv())

# remove anything above and below the quantiles
Coleoptera[which((nd_Coleoptera$LUI=="Primary vegetation") & (nd_Coleoptera$StdTmeanAnomalyRS < C_QPV[1])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Primary vegetation") & (nd_Coleoptera$StdTmeanAnomalyRS > C_QPV[2])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Secondary vegetation") & (nd_Coleoptera$StdTmeanAnomalyRS < C_QSV[1])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Secondary vegetation") & (nd_Coleoptera$StdTmeanAnomalyRS > C_QSV[2])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Agriculture_Low") & (nd_Coleoptera$StdTmeanAnomalyRS < C_QAL[1])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Agriculture_Low") & (nd_Coleoptera$StdTmeanAnomalyRS > C_QAL[2])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Agriculture_High") & (nd_Coleoptera$StdTmeanAnomalyRS < C_QAH[1])),] <- NA
Coleoptera[which((nd_Coleoptera$LUI=="Agriculture_High") & (nd_Coleoptera$StdTmeanAnomalyRS > C_QAH[2])),] <- NA

Diptera[which((nd_Diptera$LUI=="Primary vegetation") & (nd_Diptera$StdTmeanAnomalyRS < D_QPV[1])),] <- NA
Diptera[which((nd_Diptera$LUI=="Primary vegetation") & (nd_Diptera$StdTmeanAnomalyRS > D_QPV[2])),] <- NA
Diptera[which((nd_Diptera$LUI=="Secondary vegetation") & (nd_Diptera$StdTmeanAnomalyRS < D_QSV[1])),] <- NA
Diptera[which((nd_Diptera$LUI=="Secondary vegetation") & (nd_Diptera$StdTmeanAnomalyRS > D_QSV[2])),] <- NA
Diptera[which((nd_Diptera$LUI=="Agriculture_Low") & (nd_Diptera$StdTmeanAnomalyRS < D_QAL[1])),] <- NA
Diptera[which((nd_Diptera$LUI=="Agriculture_Low") & (nd_Diptera$StdTmeanAnomalyRS > D_QAL[2])),] <- NA
Diptera[which((nd_Diptera$LUI=="Agriculture_High") & (nd_Diptera$StdTmeanAnomalyRS < D_QAH[1])),] <- NA
Diptera[which((nd_Diptera$LUI=="Agriculture_High") & (nd_Diptera$StdTmeanAnomalyRS > D_QAH[2])),] <- NA

Hemiptera[which((nd_Hemiptera$LUI=="Primary vegetation") & (nd_Hemiptera$StdTmeanAnomalyRS < He_QPV[1])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Primary vegetation") & (nd_Hemiptera$StdTmeanAnomalyRS > He_QPV[2])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Secondary vegetation") & (nd_Hemiptera$StdTmeanAnomalyRS < He_QSV[1])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Secondary vegetation") & (nd_Hemiptera$StdTmeanAnomalyRS > He_QSV[2])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Agriculture_Low") & (nd_Hemiptera$StdTmeanAnomalyRS < He_QAL[1])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Agriculture_Low") & (nd_Hemiptera$StdTmeanAnomalyRS > He_QAL[2])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Agriculture_High") & (nd_Hemiptera$StdTmeanAnomalyRS < He_QAH[1])),] <- NA
Hemiptera[which((nd_Hemiptera$LUI=="Agriculture_High") & (nd_Hemiptera$StdTmeanAnomalyRS > He_QAH[2])),] <- NA

Hymenoptera[which((nd_Hymenoptera$LUI=="Primary vegetation") & (nd_Hymenoptera$StdTmeanAnomalyRS < Hy_QPV[1])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Primary vegetation") & (nd_Hymenoptera$StdTmeanAnomalyRS > Hy_QPV[2])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Secondary vegetation") & (nd_Hymenoptera$StdTmeanAnomalyRS < Hy_QSV[1])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Secondary vegetation") & (nd_Hymenoptera$StdTmeanAnomalyRS > Hy_QSV[2])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Agriculture_Low") & (nd_Hymenoptera$StdTmeanAnomalyRS < Hy_QAL[1])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Agriculture_Low") & (nd_Hymenoptera$StdTmeanAnomalyRS > Hy_QAL[2])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Agriculture_High") & (nd_Hymenoptera$StdTmeanAnomalyRS < Hy_QAH[1])),] <- NA
Hymenoptera[which((nd_Hymenoptera$LUI=="Agriculture_High") & (nd_Hymenoptera$StdTmeanAnomalyRS > Hy_QAH[2])),] <- NA

Lepidoptera[which((nd_Lepidoptera$LUI=="Primary vegetation") & (nd_Lepidoptera$StdTmeanAnomalyRS < L_QPV[1])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Primary vegetation") & (nd_Lepidoptera$StdTmeanAnomalyRS > L_QPV[2])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Secondary vegetation") & (nd_Lepidoptera$StdTmeanAnomalyRS < L_QSV[1])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Secondary vegetation") & (nd_Lepidoptera$StdTmeanAnomalyRS > L_QSV[2])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Agriculture_Low") & (nd_Lepidoptera$StdTmeanAnomalyRS < L_QAL[1])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Agriculture_Low") & (nd_Lepidoptera$StdTmeanAnomalyRS > L_QAL[2])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Agriculture_High") & (nd_Lepidoptera$StdTmeanAnomalyRS < L_QAH[1])),] <- NA
Lepidoptera[which((nd_Lepidoptera$LUI=="Agriculture_High") & (nd_Lepidoptera$StdTmeanAnomalyRS > L_QAH[2])),] <- NA


# Get the median, upper and lower quants for the plot

nd_Coleoptera$PredMedian <- ((apply(X = Coleoptera,MARGIN = 1,
                                    FUN = median,na.rm=TRUE))*100)-100
nd_Coleoptera$PredUpper <- ((apply(X = Coleoptera,MARGIN = 1,
                                   FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Coleoptera$PredLower <- ((apply(X = Coleoptera,MARGIN = 1,
                                   FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd_Diptera$PredMedian <- ((apply(X = Diptera,MARGIN = 1,
                                 FUN = median,na.rm=TRUE))*100)-100
nd_Diptera$PredUpper <- ((apply(X = Diptera,MARGIN = 1,
                                FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Diptera$PredLower <- ((apply(X = Diptera,MARGIN = 1,
                                FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd_Hemiptera$PredMedian <- ((apply(X = Hemiptera,MARGIN = 1,
                                   FUN = median,na.rm=TRUE))*100)-100
nd_Hemiptera$PredUpper <- ((apply(X = Hemiptera,MARGIN = 1,
                                  FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Hemiptera$PredLower <- ((apply(X = Hemiptera,MARGIN = 1,
                                  FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd_Hymenoptera$PredMedian <- ((apply(X = Hymenoptera,MARGIN = 1,
                                     FUN = median,na.rm=TRUE))*100)-100
nd_Hymenoptera$PredUpper <- ((apply(X = Hymenoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Hymenoptera$PredLower <- ((apply(X = Hymenoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100

nd_Lepidoptera$PredMedian <- ((apply(X = Lepidoptera,MARGIN = 1,
                                     FUN = median,na.rm=TRUE))*100)-100
nd_Lepidoptera$PredUpper <- ((apply(X = Lepidoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.975,na.rm=TRUE))*100)-100
nd_Lepidoptera$PredLower <- ((apply(X = Lepidoptera,MARGIN = 1,
                                    FUN = quantile,probs = 0.025,na.rm=TRUE))*100)-100


# set factor levels
nd_Coleoptera$LUI <- factor(nd_Coleoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd_Diptera$LUI <- factor(nd_Diptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd_Hemiptera$LUI <- factor(nd_Hemiptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd_Hymenoptera$LUI <- factor(nd_Hymenoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))
nd_Lepidoptera$LUI <- factor(nd_Lepidoptera$LUI, levels = c("Primary vegetation", "Secondary vegetation", "Agriculture_Low", "Agriculture_High"))

# plot

p_coleoptera <- ggplot(data = nd_Coleoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Coleoptera$PredLower, ymax = nd_Coleoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") + 
  ggtitle("Coleoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none", 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25)) 
  

p_diptera <- ggplot(data = nd_Diptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Diptera$PredLower, ymax = nd_Diptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Diptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none", 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25)) 
  

p_hemiptera <- ggplot(data = nd_Hemiptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Hemiptera$PredLower, ymax = nd_Hemiptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Hemiptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25))
  

p_hymenoptera <- ggplot(data = nd_Hymenoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Hymenoptera$PredLower, ymax = nd_Hymenoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Hymenoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none", 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25))

p_lepidoptera <- ggplot(data = nd_Lepidoptera, aes(x = StdTmeanAnomaly, y = PredMedian)) + 
  geom_line(aes(col = LUI), size = 0.75) +
  geom_ribbon(aes(ymin = nd_Lepidoptera$PredLower, ymax = nd_Lepidoptera$PredUpper, fill = LUI), alpha = 0.2) +
  geom_hline(yintercept = 0, lty = "dashed", size = 0.25) +
  scale_fill_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  scale_colour_manual('Land-use', values = c("#009E73", "#0072B2","#E69F00","#D55E00")) +
  theme_bw() + 
  scale_x_continuous(breaks = c(0,0.5, 1, 1.5, 2), limits = c(0, 2)) +
  #scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(-100,-75, -50, -25, 0, 25, 50, 75, 100, 125,150,175), limits = c(-100, 175)) +
  ylab("Change in total abundance (%)") +
  xlab("Standardised Temperature Anomaly") +
  ggtitle("Lepidoptera") +
  theme(aspect.ratio = 1, 
        plot.title = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 7),
        axis.ticks = element_line(size = 0.25),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.25),
        panel.border = element_rect(size = 0.25)) 
  

# get the legend
legend <- get_legend(
  p_coleoptera +
    guides(color = guide_legend(ncol = 1)) +
    theme(legend.position = "right",
          legend.background = element_blank(), 
          legend.text = element_text(size = 7), 
          legend.title = element_blank())
)



tit <- ggdraw() + 
        draw_label(paste0("Excluding studies where the difference in anomaly values is more than ", i ))

# put them all together to save them
MeanAnomAbund <- cowplot::plot_grid(p_coleoptera,p_diptera,p_hemiptera,p_hymenoptera,p_lepidoptera,legend, ncol = 3)
MeanAnomAbund <- cowplot::plot_grid(tit, MeanAnomAbund, nrow = 2, rel_heights =c(0.1,1))

MeanAnomAbund


# save plot (pdf)
ggsave(filename = paste0(outdir, "MeanAnomalyModelAbund_excl_", i, ".pdf"), plot = MeanAnomAbund, width = 200, height = 150, units = "mm", dpi = 300)

# save plot (jpeg)
ggsave(paste0("MeanAnomalyModelAbund_excl_", i, ".jpeg"), device ="jpeg", path = outdir, width=20, height=15, units="cm", dpi = 350)



  
}










```

The plots are not presented here. 


























